Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-08-26 tensor/draft/draft-tensor-op.tex
[draft-tensor-op] modified eq.(3.1), final version arXiv v1
[draft-tensor-op.tex] changed name of A_\Delta\Gamma(B_s -> mu mu) to mass-eigenstate rate asymmetry as suggested by referee and unified symbol {\cal A} -> A around eq.(A.8)

\date{\today}
\maketitle

@@

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensor and
scalar couplings has been presented in \cite{Bobeth:2007dw,
  Bobeth:2012vn}, adopting the effective theory \refeq{eq:Heff},
i.e. neglecting higher-dimensional operators with {$\mbox{dim} \geq
  8$}. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}
    {\bigg/ \Gamma_\ell} \,, &
  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.
The flat term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed {by
  small lepton masses for the considered kinematic region $1 \leq
  q^2 \leq 22$ GeV$^2$} \cite{Bobeth:2007dw, Bobeth:2011nj,
  Bouchard:2013eph}.  Nonzero values of $A_{\rm FB}^\ell|_{\rm SM}$
can be induced by higher-order QED corrections, which will modify the
simple $\cos\theta_\ell$ dependence of the angular
distribution~\refeq{eq:ang-distr}, however, currently there is no
solid estimate available for this source of SM background\footnote{
  Logarithmically enhanced NLO QED corrections to $B\to X_s
  \bar\ell\ell$~\cite{Huber:2015sra} turn out to be non-negligible
  for angular observables,
  however, analogous corrections to $B\to K \bar\ell\ell$ are partially
  included in the event simulation of the experimental
  analysis~\cite{Aaij:2014tfa} via PHOTOS~\cite{Golonka:2005pn}.
  As proposed in \cite{Gratrex:2015hna}, the measurement of higher
  moments of the decay distribution~\refeq{eq:ang-distr} could give an
  estimate of the size of higher-order QED corrections, but still
  admixed with contributions of $\mbox{dim} \geq 8$ operators.}.
This picture does not change in the presence of new physics contributions to
vector and dipole operators $i = 7,7',9,9',10,10'$. On the other hand,
nonvanishing tensor or scalar contributions are enhanced unless the dynamics of
NP implies similar suppression factors, i.e., lepton-Yukawa couplings for
$F_H^\ell$ or $\alpha_e$ in the case of $A_{\rm FB}^\ell$. In particular,
$F_H^\ell$ is very sensitive to tensor couplings (see \refeq{eq:AFB-dependence}
below) and $A_{\rm FB}^\ell$ is sensitive to the interference of tensor and
scalar couplings (see \refeq{eq:FH-dependence} below).

@@

For the CP asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ induced by
the nonvanishing width of the $B_s$ meson
(cf. \refapp{app:BKstarellell}), we find a rather uniform distribution
in scenarios with nonzero scalar couplings. So any value in the range
$[-1,\, 1]$ is plausible whereas {the SM and the scenario
  with only tensor couplings predict a value of precisely one
  \cite{DeBruyn:2012wk}}; cf. the last row in
\reftab{tab:postdictions}. Hence any deviation from one would
unambiguously hint at the presence of scalar operators.

@@

Our study of the {yet unmeasured} angular observables $J_{6c}$,
$(J_{1c} + J_{2c})$, and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi)
\bar\mu\mu$ (see \reftab{tab:postdictions}) shows that despite the
current bounds on tensor couplings, enhancements of up to two orders
of magnitude over the SM predictions are allowed for $(J_{1c} +
J_{2c})$ and $(J_{1s} - 3 J_{2s})$, placing them in reach of the LHCb
analysis of the full run~I data set. Our bounds on scalar couplings
from $B_s\to \bar\mu\mu$ and $F_H^\mu$, however, are already quite
restrictive permitting only small deviations from SM predictions in
$(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$. Notably, the CP
asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ given nonzero scalar
couplings can take on any value in the range $[-1,\, 1]$.

@@

  Concerning $B_s\to \bar\ell\ell$, the expression \refeq{eq:Br-Bsmumu:time0}
  corresponds to the plain branching ratio at time $t=0$. Due to the
  nonvanishing decay width $\Delta\Gamma_s$, experiments measure the average
  time-integrated branching ratio---denoted by $\overline{\cal B}$---and the two
  are related as \cite{DeBruyn:2012wk}
\begin{align}
  \label{eq:Br-Bsmumu}
  \overline{\cal B} (B_s \to \bar\ell\ell) &
  = \frac{1 + y_s {\cal A}_{\Delta\Gamma}}{1 - y_s^2} {\cal B} (B_s \to \bar\ell\ell)\,.
\end{align}
Here $y_s \equiv \Delta\Gamma_s/(2\Gamma_s)$ with the numerical value given in
\cite{Beaujean:2013soa}. ${\cal A}_{\Delta\Gamma}$ is the CP asymmetry
due to nonvanishing width difference, which is ${\cal A}_{\Delta\Gamma} = 1$
in the SM, but in general can be ${\cal A}_{\Delta\Gamma} \in [-1,\, 1]$.
Since ${\cal A}_{\Delta\Gamma}$ can depart from it's SM value in scenarios of
new physics considered in this work, we take this effect into account
in our numerical analysis, although it is suppressed by small $y_s$. The latest
SM prediction $\overline{\cal B} (B_s \to \bar\mu\mu) = (3.65 \pm 0.23) \cdot
10^{-9}$~\cite{Bobeth:2013uxa} includes NLO electroweak \cite{Bobeth:2013tba}
and NNLO QCD corrections \cite{Hermann:2013kca}.

>>>>

%\date{\today}
\maketitle

@@

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensor and
scalar couplings has been presented in \cite{Bobeth:2007dw,
  Bobeth:2012vn}, adopting the effective theory \refeq{eq:Heff},
i.e. neglecting higher-dimensional operators with {$\mbox{dim} \geq
  8$}. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}
    \bigg/ \Gamma_\ell(q^2) \,, &
  A_{\rm FB}^\ell(q^2) \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.
The flat term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed {by
  small lepton masses for the considered kinematic region $1 \leq
  q^2 \leq 22$ GeV$^2$} \cite{Bobeth:2007dw, Bobeth:2011nj,
  Bouchard:2013eph}.  Nonzero values of $A_{\rm FB}^\ell|_{\rm SM}$
can be induced by higher-order QED corrections, which will modify the
simple $\cos\theta_\ell$ dependence of the angular
distribution~\refeq{eq:ang-distr}, however, currently there is no
solid estimate available for this source of SM background\footnote{
  Logarithmically enhanced NLO QED corrections to $B\to X_s
  \bar\ell\ell$~\cite{Huber:2015sra} turn out to be non-negligible
  for angular observables,
  however, analogous corrections to $B\to K \bar\ell\ell$ are partially
  included in the event simulation of the experimental
  analysis~\cite{Aaij:2014tfa} via PHOTOS~\cite{Golonka:2005pn}.
  As proposed in \cite{Gratrex:2015hna}, the measurement of higher
  moments of the decay distribution~\refeq{eq:ang-distr} could give an
  estimate of the size of higher-order QED corrections, but still
  admixed with contributions of $\mbox{dim} \geq 8$ operators.}.
This picture does not change in the presence of new physics contributions to
vector and dipole operators $i = 7,7',9,9',10,10'$. On the other hand,
nonvanishing tensor or scalar contributions are enhanced unless the dynamics of
NP implies similar suppression factors, i.e., lepton-Yukawa couplings for
$F_H^\ell$ or $\alpha_e$ in the case of $A_{\rm FB}^\ell$. In particular,
$F_H^\ell$ is very sensitive to tensor couplings (see \refeq{eq:AFB-dependence}
below) and $A_{\rm FB}^\ell$ is sensitive to the interference of tensor and
scalar couplings (see \refeq{eq:FH-dependence} below).

@@

For the \christoph{mass-eigenstate rate} asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ induced by
the nonvanishing width of the $B_s$ meson
(cf. \refapp{app:BKstarellell}), we find a rather uniform distribution
in scenarios with nonzero scalar couplings. So any value in the range
$[-1,\, 1]$ is plausible whereas {the SM and the scenario
  with only tensor couplings predict a value of precisely one
  \cite{DeBruyn:2012wk}}; cf. the last row in
\reftab{tab:postdictions}. Hence any deviation from one would
unambiguously hint at the presence of scalar operators.

@@

Our study of the {yet unmeasured} angular observables $J_{6c}$,
$(J_{1c} + J_{2c})$, and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi)
\bar\mu\mu$ (see \reftab{tab:postdictions}) shows that despite the
current bounds on tensor couplings, enhancements of up to two orders
of magnitude over the SM predictions are allowed for $(J_{1c} +
J_{2c})$ and $(J_{1s} - 3 J_{2s})$, placing them in reach of the LHCb
analysis of the full run~I data set. Our bounds on scalar couplings
from $B_s\to \bar\mu\mu$ and $F_H^\mu$, however, are already quite
restrictive permitting only small deviations from SM predictions in
$(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$. Notably, the \christoph{
mass-eigenstate rate}
asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ given nonzero scalar
couplings can take on any value in the range $[-1,\, 1]$.

@@

  Concerning $B_s\to \bar\ell\ell$, the expression \refeq{eq:Br-Bsmumu:time0}
  corresponds to the plain branching ratio at time $t=0$. Due to the
  nonvanishing decay width $\Delta\Gamma_s$, experiments measure the average
  time-integrated branching ratio---denoted by $\overline{\cal B}$---and the two
  are related as \cite{DeBruyn:2012wk}
\begin{align}
  \label{eq:Br-Bsmumu}
  \overline{\cal B} (B_s \to \bar\ell\ell) &
  = \frac{1 + y_s \christoph{\, A_{\Delta\Gamma}}}{1 - y_s^2} {\cal B} (B_s \to \bar\ell\ell)\,.
\end{align}
Here $y_s \equiv \Delta\Gamma_s/(2\Gamma_s)$ with the numerical value given in
\cite{Beaujean:2013soa}. \christoph{$A_{\Delta\Gamma}$ is the mass-eigenstate rate} asymmetry
due to nonvanishing width difference, which is \christoph{$A_{\Delta\Gamma} = 1$}
in the SM, but in general can be \christoph{$A_{\Delta\Gamma} \in [-1,\, 1]$}.
Since \christoph{$A_{\Delta\Gamma}$} can depart from it's SM value in scenarios of
new physics considered in this work, we take this effect into account
in our numerical analysis, although it is suppressed by small $y_s$. The latest
SM prediction $\overline{\cal B} (B_s \to \bar\mu\mu) = (3.65 \pm 0.23) \cdot
10^{-9}$~\cite{Bobeth:2013uxa} includes NLO electroweak \cite{Bobeth:2013tba}
and NNLO QCD corrections \cite{Hermann:2013kca}.
